---
title: "Untitled"
self-contained: true
format: html
editor: visual
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE
)
library(tidyverse)
library(glue)
library(readr)
Sked <- read_csv('full_schedule_2022-10-25T11_38_50-04_00.csv')
```

```{r results = 'asis'}
Sked |> glue_data(
"

## {SubjectCode} {CourseNum} {SectionCode}

**Start:** {SectionStartDate}
**End:** {SectionEndDate}

**Title:** {ShortTitle}

**Capacity** (Global Max): {GlobalMax}


**Notes:** {Comments}

**Faculty Load:**  |  **Semester Hours ** |  **Delivery mode:**     
-------------------|--------------------|------------------------
{`FacultyLoad`}    |  {MinimumCredits}  | {InstructionalMethod}

**Instructor(s)**: {Faculty}

**Meeting Pattern**: {MeetingDays} {MeetingTime}

") |>
  cat()
```

Section name: MATH 171 A
Start/end dates
Title
Fac Load
Section Capacity
Sem Hours
Notes to be shown to stu/faculty (if there are any)– this requires clicking on the section from Find Course Sections
Delivery mode: in person, online, hybrid (rare)
Instructor(s)
Meeting Pattern – which is days then time
 
Instructional format defaults from the course (lecture, lab, etc) so we don’t need that information – or it could be to the far right.