---
title: "Data for Entry into Workday"
self-contained: true
format: 
  html:
    css: schedulizer.css
editor: visual
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE
)
library(tidyverse)
library(glue)
library(readr)
Sked <- read_csv('full_schedule_2022-10-25T11_38_50-04_00.csv')
```

```{r results = 'asis'}
Sked |> 
  mutate(Term = substr(Term, 4, 5)) |>
  mutate(Faculty = gsub("\n", " | ", Faculty)) |>
  mutate(MeetingTime = gsub("\n", " | ", MeetingTime)) |>
  mutate(BuildingAndRoom = gsub("\n", " | ", BuildingAndRoom)) |>
  mutate(FacultyLoad = gsub("\n", " | ", FacultyLoad)) |>
  mutate(MinimumCredits = gsub("\n", " | ", MinimumCredits)) |>
  mutate(Comments = ifelse(is.na(Comments), "", Comments)) |>
  glue_data(
"

<div class = \"course-section\">

<table>
<tr>
<th>Section </th>
<th>Term </th>
<th>Time </th>
<th>Room </th>
<th>Capacity </th>
<th>FLH</th>
<th>SLH</th>
<th>Mode</th>
</tr>
<tr>
<td>{SubjectCode} {CourseNum} {SectionCode} </td>
<td>{Term} -- {SemesterLength} </td>
<td>{MeetingDays} {MeetingTime} </td>
<td>{BuildingAndRoom} </td>
<td>{GlobalMax} </td>
<td> {FacultyLoad} </td>
<td> {MinimumCredits} </td>
<td>{InstructionalMethod} </td>
</tr>
</table>

<table>
<tr>
<td> **Short Title:** {ShortTitle} </td>
<td> **Instructor(s)**: {Faculty}</td>
</tr>
</table>

{Comments}
</div>
") |>
  cat()
```

Section name: MATH 171 A Start/end dates Title Fac Load Section Capacity Sem Hours Notes to be shown to stu/faculty (if there are any)-- this requires clicking on the section from Find Course Sections Delivery mode: in person, online, hybrid (rare) Instructor(s) Meeting Pattern -- which is days then time

Instructional format defaults from the course (lecture, lab, etc) so we don't need that information -- or it could be to the far right.
